A Control Strategy for a Tethered Follower Robot for Pulmonary Rehabilitation

### 2020-10-16 review2/response.letter.tex

\section*{\fbox{Reviewer \#2 Responses:}}
%\subsection*{\ovalbox{Reviewer 2 General Comments}}

The revisions the authors have made have improved the manuscript - thank you for implementing those. At this stage, I have a few remaining concerns.

- The word definitions of $l_R$ and $l_L$ are still unclear. They are introduced as differences in length, but then also referred to as "thread longitudes". I find the term "longitude" here to be confusing given that these length differences can have a non-horizontal component if the target is at some angle from the reel (i.e., they are not purely longitudinal measurements, but rather can be seen as two vectors pointing to the same point in 2D space with both x and y components). My recommendation is that these definitions be further clarified.

\vspace{10pt} 
\begin{quotation}
{\color{blue}
We have modified on Section II.D, at the end of page 3, and clarified the terms according to the Reviewer's suggestion.  These terms are indeed changes in the length of the thread released from each reel.  We have eliminated the use of the confusing term "longitude".  
}
\end{quotation}
\vspace{10pt}

@@

- In Algorithm 1, as far as I can tell, no definition is provided for $D_t$, $D_m$, nor $base_{vr}$. This should be remedied.

\vspace{10pt} 
\begin{quotation}
{\color{blue}
We have included in Section II, page 4, the definition of $base_{vr}$ which was missing, and also clarified that $D_t$, $D_m$ are temporary variables used to perform the calculations on Algorithm 1.
}
\end{quotation}
\vspace{10pt}

- I believe Section III B. can be improved by being even more explicit about the specific improvements in the current design vs. the existing design. Section III, in general, reads as-if these designs are just equivalent (which begs the question: "why was this work done then?")

\vspace{10pt} 
\begin{quotation}
{\color{blue}
This is an excellent question.  We have modified Section III.B emphasizing the two aspects that we think justify our proposal.  As described there, the first one is related with the active spring system that we are proposing.  We think it is more appropriate for patients that have stringent requirements related to how they move.   One important aspect of our approach is that the stiffness and other mechanical properties can be regulated directly by software due to the active control mechanism based on motors.   The second aspect, is that for pulmonary rehabilitation procedures, the design that we propose emphasizes the local calculation of the patient position based on the sensing information obtained from the differential-tethered mechanism.  However, other approaches, propose dead-reckoning to do so, which may induce cumulative errors that would require frequent interruptions to re-calibrate the system.   
We have added more details regarding these issues in the above-mentioned Section and also included relevant references on Section II.C (Active Reel Spring).
}
\end{quotation}
\vspace{10pt}

### 2020-10-16 alpibot.tex
Subo la versión que mandamos para la 3ra vuelta.

As previously mentioned, an active spring mechanism is also put in place to keep the threads tense.  However, in order to extend the useful life of the reel motors, and to save battery, an algorithm to  activate and deactivate the motors was developed.

@@

In the scheme proposed by~\cite{Endo2015} a single thread is recovered mechanically by means of a circular flat spring. This device works intensively when the robot is following the patient and, therefore, the spring is exposed to wear. Additionally with a circular flat spring, the spring tension depends on the released thread length, hence the recovery force will vary accordingly. Instead, the double thread tethered design implemented with an active reel spring allows a more controlled situation and depends exclusively on the software that controls the reel motor, which can be regulated.

Regarding the control algorithm, authors in \cite{Endo2015} introduced two methods. The first of them computes the angular velocity as a  function of the difference between the measured thread length $l_m$ and the desired distance to patient  $l_D$. In this way, if the patient moves around the robot with a $l_m$ equals to $l_D$, the robot will not adjust its direction until the patient stops turning and restarts moving forward. Hence, the robot must correct its direction but the correction angle could be large, which leads the robot to deviate off the desired trajectory. Additionally, the second method proposed is based on dead-reckoning to estimate the patient position. This strategy requires very precise measurements to reduce the cumulative error, which is characteristic of this estimation procedure~\cite{DurrantWhyte1994}.

>>>>

As previously mentioned, an active spring~\cite{Vanderborght2013} mechanism is also put in place to keep the threads tense.  However, in order to extend the useful life of the reel motors, and to save battery, an algorithm to  activate and deactivate the motors was developed.

@@

In the scheme proposed by~\cite{Endo2015} a single thread is recovered mechanically by means of a circular flat spring. This device works intensively when the robot is following the patient and, therefore, the spring is exposed to wear. Additionally with a circular flat spring the properties of the spring components are predefined by their structural preconditions, and cannot be altered during spring operation~\cite{wurmthaler2013apparatus}. For instance, the spring tension depends on the released thread length, hence the recovery force will vary accordingly.  If the patient found this tension to be too tight, it is not possible to alter this behavior without structurally modifying the device, or changing the spring component altogether.  Instead, the double thread tethered design implemented with an active reel spring allows a more controlled situation and depends exclusively on the software that controls the reel motor, which can be regulated.

Regarding the control algorithm, authors in \cite{Endo2015} introduced two methods. The first of them computes the angular velocity as a function of the difference between the measured thread length $l_m$ and the desired distance to patient  $l_D$. In this way, if the patient moves around the robot with a $l_m$ equals to $l_D$, the robot will not adjust its direction until the patient stops turning and restarts moving forward. Hence, the robot must correct its direction but the correction angle could be large, which leads the robot to deviate off the desired trajectory. Additionally, the second method proposed is based on dead-reckoning to estimate the patient position. It is well stated~\cite{DurrantWhyte1994} that position estimation using dead-reckoning leads to an increasing error along cumulative distance with continuous changes of angular velocity. This presents a limitation to hold therapy sessions with patients who need to cover standard trajectory distances, requiring more frequent interruptions to perform calibration procedures.
